Type Refinements for the Working Class

### 2015-12-22 paper.tex
typo

The dependent intersection, first introduced by Kopylov in \cite{kopylov:2000},
are a generalization of the binary intersection to the dependent case, not to
be confused with the intersection of a family of sets. The dependent
intersection has many applications, including the compositional representation
of \emph{dependent records} or modules in Type Theory.

>>>>

The dependent intersection, first introduced by Kopylov in \cite{kopylov:2000},
is a generalization of the binary intersection to the dependent case, not to
be confused with the intersection of a family of sets. The dependent
intersection has many applications, including the compositional representation
of \emph{dependent records} or modules in Type Theory.
